---
title: "Linear Regression - Credit Card Purchases"
author: "Christian Thomas Schmidt"
date: "2/8/2022"
output: html_document
---

# Linear Regression Project - Credit Card Purchases

## Preview

In this project, I will be analyzing my spending over the last 7 months.
The goal of this project is to understand If I am spending more or less 
over time and what a linear regression model predicts my spending will be next month.<br></br>

The data set I am using is from own card activity. 

## Libraries

The libraries I will be using are as follows:

```{r setup, include=TRUE,warning=FALSE,results=FALSE,message=FALSE}

library(tidyverse)
library(lubridate)


```

```{r hidden setwd, include=FALSE,}
setwd("C:/Users/cschm/OneDrive/Desktop/Data Science Projects/Linear Regression/Credit Card Information")
```


## Data Exploration

I will first want to see a quick overview of the data

```{r download and analyze data, echo=TRUE,results=FALSE,warning=FALSE,message=FALSE}

# Download data
new_df <- read_csv('credit_card_purchases.csv')

```

```{r summary, include=TRUE,warning=FALSE}

# summary of data frame and head()
dim(new_df)
str(new_df)
```

Looking at the data, I can see that data consists of 6 different columns.<p>
<ul>
  <li>Transaction Date</li>
  <li>Post Date</li>
  <li>Description</li>
  <li>Category</li>
  <li>Type</li>
  <li>Amount</li>
</ul><p>

I want to transform this data to make it easier for me to run my model.<p>

Given that I am only interested in what day the transaction was, the category of purchase and the amount the purchase was, 
I will remove Post Date, Description, and Type from the data frame.<p> 

I also want to change the data type for both "Category" and "Transaction Date".
I will change the data type of Category from character to non-ordinal factor and "Transaction Date" into date format.<p>

I also don't care what day of the month I made a purchase, but rather what <i>month</i> I made that purchase and what year.
I will mutate "Transaction Date" into two new columns, "Year" and "Month"

```{r updated df, echo=TRUE,results=TRUE,warning=FALSE,message=FALSE}

df <- new_df %>%
  select(`Transaction Date`,Category,Amount) %>%
  mutate(Date = lubridate::mdy(`Transaction Date`),.before = Category) %>%
  mutate(Month = lubridate::month(Date,label = TRUE, abbr = TRUE),.after = Date) %>%
  mutate(Year = lubridate::year(Date),.after = Date) %>%
  group_by(Date) %>%
  select(-`Transaction Date`)

# "Category" is now a factor
df$Category <- factor(df$Category)
unique(df$Category)

head(df)

```

Before I build my model, I want to quickly examine which category is my most <b>expensive</b> category to-date.
I do this by summarizing the amount for each category in an array. I noticed that some purchases are also listed under "NA" and I want to find out more about this category.



```{r summarize data, echo=TRUE,results=TRUE,warning=FALSE,message=FALSE}

df_summary <- df %>%
  group_by(Category) %>%
```

